### 2023-06-13 manuscript.tex
bibliography fixes from thesis [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/d590b21d8a5e9afb5e0df414044044c16f5afcb9.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/d590b21d8a5e9afb5e0df414044044c16f5afcb9/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5261086824

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/12c36282be545d60358eeed915d0e52941a16774/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/12c36282be545d60358eeed915d0e52941a16774}{stain/2022-fdo-paper@12c3628}
on June 13, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/d590b21d8a5e9afb5e0df414044044c16f5afcb9/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/d590b21d8a5e9afb5e0df414044044c16f5afcb9}{stain/2022-fdo-paper@d590b21}
on June 13, 2023.
